Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_3_model.tex
Work on dynamic convolution section

A high level image representation is obtained with a
ResNet-152~\cite{He2016ResNet} model pre-trained on ImageNet. We use the output
of the final block before the
pooling layer as the image representation.
This is set of 49 different vectors $x_{I,i} \in \mathbb{R}^{2048}$ where each
vector corresponds to a separate image patch after the image is divided into
equal size 7 by 7 patches. Using this representation $\bx_I = \{x_{I,i} \in
\mathbb{R}^{2048}\}_{i=0}^{49}$ allows the decoder to attend different regions
in the
image -- a modelling choice that has proven useful in other image captioning
tasks~\cite{Xu2015ShowAA}.

@@

We use MTCNN \cite{Zhang2016JointFD} to detect face bounding boxes in the
image. We then select the largest $M$ faces. A vector representation of each
face is obtained by passing the bounding boxes to
FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
image is $\bx_{F} = \{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=0}^M$.

@@

One limitation of RoBERTa is that the maximum length of the input sequence is
512. For GoodNews, we simply encode the first 512 tokens of the article. For
NYTimes800k, since we have the image position, we concatenate the title, the
first paragraph, and as many paragraphs above and below the image as we can
fit, until we reach the 512 token limit. Note that since we are using BPE, a
word might consist of many tokens. On average, we can only encode ...... words
of the article.

The RoBERTa encoder provides gives us the article embedding $\bX_T \in
\mathbb{R}^{1024 \times S}$ where $S$ is the number of tokens.

\subsubsection{Face Embedding}

To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
face bounding boxes. We then select the top $M$ faces and feed them through a
FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bX_F \in
\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.

@@

The decoder is a function that estimates $p(y_t)$, the probability of the next
token, conditional on the past $\by_{<t}$ and the context embeddings $\bX_I$,
$\bX_T$, and $\bX_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bX_I, \bX_T, \bX_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four layers of transformer blocks.
In each block, the conditioning on past tokens is computed using dynamic
convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
computed using multi-head attention \cite{Vaswani2017AttentionIA}.

@@

Let $\bh_t \in \mathbb{R}^{1024}$ be the current hidden state when decoding the
$t$th token. We use 16 attention heads, each with size 64. For each head $i \in
\{1, 2, ..., 16\}$, we first do a linear projection of $\bh_t$ and the image
embedding $\bX_I$ into a query $\bq_{It} \in \mathbb{R}^{64}$, key $\bK_I \in
\mathbb{R}^{64 \times 49}$, and value $\bV_I \in \mathbb{R}^{64 \times 49}$:
\begin{IEEEeqnarray*}{lCl}
   \bq_{Iit} &=& \bW_{Iiq} \, \bh_t \\
   \bK_{Ii} &=& \bW_{Iik} \, \bX_I \\
   \bV_{Ii} &=& \bW_{Iiv} \, \bX_I
\end{IEEEeqnarray*}
Then the attended image for each head $\bx'_{Ii} \in \mathbb{R}^{64}$ is the
weighted sum of the values, where the weights are obtained from the dot product
between the query and key:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{Ii} &=& \text{softmax}\left(\bK_{Ii}^T \bq_{Iit} \right) \bV_{Ii}
\end{IEEEeqnarray*}
The attention from each head is then concatenated into $\bx'_{I} \in
\mathbb{R}^{1024}$:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{I} &=& [\tx_{I1}, \tx_{I2}, ..., \tx_{I16}]
\end{IEEEeqnarray*}
and the overall image attention $\tx_{I} \in \mathbb{R}^{1024}$ is obtained
after adding a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tx_{I} &=& \text{LayerNorm}(\bh_t + \bx'_{I})
\end{IEEEeqnarray*}
We use the same attention mechanism (with different weight matrices) to obtain
the attended article $\tx_T$ and the attended face $\tx_F$. These three are
then concatenated and fed through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \tx_C &=& [\tx_I, \tx_T, \tx_F] \\
   \tx_R &=& \bW_C \, \tx_C + \bb_C \\
   \tx_D &=& \text{ReLU}(\bW_R \, \tx_R + \bb_R )\\
   \tx_E &=& \text{LayerNorm}(\tx_R + \bW_D \, \tx_D + \bb_D)
\end{IEEEeqnarray*}
The final output $\tx_E \in \mathbb{R}^{1024}$ is used as the input to the
next transformer block.

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 architecture \cite{Radford2019LanguageMA}, we find that
dynamic convolutions \cite{Wu2018PayLA} are more efficient to train. Suppose
when decoding the $t$th token, we have an input $\bz_t \in \mathbb{R}^{1024}$,
which can either be the input embedding of the previous token, or the output
from the previous transformer block. Given kernel size $K$, we first do a
projection of the last $K$ steps using a feedforward layer with a gated linear
unit (GLU) \cite{Dauphin2017GLU} as the activation function:
\begin{IEEEeqnarray*}{lCl}
   \bz_{t-j}' &=& \text{GLU}(\bW_Z \, \bz_{t-j} + \bb_Z) \qquad \forall j \in \{0,1,...,K-1\}
\end{IEEEeqnarray*}
the output of the dynamic convolution is simply the weighted sum of these
projected values:
\begin{IEEEeqnarray*}{lCl}
   \tz_t &=& \sum_0^{K-1}
\end{IEEEeqnarray*}

We use 16 attention heads, each with size 64. For each head $i \in
\{1, 2, ..., 16\}$, we first do a linear projection to get the kernel weight
\begin{IEEEeqnarray*}{lCl}
   \bW \, \bz_t'
\end{IEEEeqnarray*}

\subsection{Bag of Tricks}

>>>>

A high level image representation is obtained with a
ResNet-152~\cite{He2016ResNet} model pre-trained on ImageNet. We use the output
of the final block before the pooling layer as the image representation. This
is a set of 49 different vectors $\bx_{I,i} \in \mathbb{R}^{2048}$ where each
vector corresponds to a separate image patch after the image is divided into
equal size 7 by 7 patches. Using this representation $\bX_I = \{\bx_{I,i} \in
\mathbb{R}^{2048}\}_{i=1}^{49}$ allows the decoder to attend different regions
in the image---a modeling choice that has proven useful in other image
captioning tasks~\cite{Xu2015ShowAA}.

@@

We use MTCNN~\cite{Zhang2016JointFD} to detect face bounding boxes in the
image. We then select the largest four faces (see \ref{ssec:nytimes800k}). A
vector representation of each face is obtained by passing the bounding boxes to
FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
image is $\bx_{F} = \{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=1}^4$.

@@

One limitation of RoBERTa is that the maximum length of the input sequence is
512. For GoodNews, we simply encode the first 512 tokens of the article. For
NYTimes800k, since we have the image position, we concatenate the title, the
first paragraph, and as many paragraphs above and below the image as we can
fit, until we reach the 512 token limit. Note that since we are using BPE, a
word might consist of many tokens. On average, \verify{we can only encode
...... words of the article.}

The RoBERTa encoder provides gives us the set of token embeddings $\bX_{T} =
\{\bx_{T,i} \in \mathbb{R}^{1024}\}_{i=1}^S$, where $S$ is the number of
tokens.

@@

The decoder is a function that estimates $p(y_t)$, the probability of the $t$th
token in the caption, conditional on the past $\by_{<t}$ and the context
embeddings $\bX_I$, $\bX_T$, and $\bX_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bX_I, \bX_T, \bX_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four layers of transformer blocks.
In each block, the conditioning on past tokens is computed using dynamic
convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
computed using multi-head attention \cite{Vaswani2017AttentionIA}.

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 decoder \cite{Radford2019LanguageMA}, we find that
dynamic convolutions \cite{Wu2018PayLA} are more efficient to train. Suppose
when decoding the $t$th token, we have at the $\ell$th block the input
$\bz_{\ell t} \in \mathbb{R}^{1024}$. If $\ell = 0$, then $\bz_{0t}$ is the
embedding of the previous token. Otherwise it is the output from the previous
transformer block. Given kernel size $K$ and 16 attention heads, for each head
$h \in \{1, 2, ..., 16\}$, we first project the current and last $K-1$ steps
using a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bz_{\ell,h,t-j}' &=& \text{GLU}(\bW_{z\ell h} \, \bz_{\ell,t-j} + \bb_{z\ell h})
\end{IEEEeqnarray*}
where $j \in \{0,1,...,K-1\}$, GLU is the gated linear unit activation
function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
The output of the dynamic convolution of each head is simply the weighted sum
of these projected values:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell h t} &=& \sum_{j=0}^{K-1} \gamma_{\ell hj} \, \bz_{\ell, h, t-j}'
\end{IEEEeqnarray*}
where the weights $\gamma_{\ell hj}$ is a linear projection of the input,
followed by a softmax over the kernel window:
\begin{IEEEeqnarray*}{lCl}
   \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
      \bz_{\ell,h,t-j} \right)
\end{IEEEeqnarray*}
The overall output is the concatenation of all the head outputs, followed by
a feedforward with a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell t} &=& [ \tz_{\ell 1 t}, \tz_{\ell 2 t},..., \tz_{\ell 16 t} ] \\
   \bd_{\ell t} &=& \text{LayerNorm}\left( \bz_{\ell t} +
             \bW_{\tz \ell} \, \tz_{\ell t} + \bb_{\tz \ell} \right)
\end{IEEEeqnarray*}
Note that given kernel size $K$, we can attend to the current time step and the
last $K-1$ steps. Following closely to \cite{Wu2018PayLA}, our decoder has 4
layers with kernel sizes 3, 7, 15, and 31, respectively. Thus the final layer
output will have collected information from the last 51 tokens.

@@

Let $\bd_{\ell t} \in \mathbb{R}^{1024}$ be the output of the dynamic
convolution. We now attend over the image context using multi-head attention,
also with 16 heads. For each head $h \in \{1, 2, ..., 16\}$, we first do a
linear projection of $\bd_{\ell t}$ and the image embeddings $\bX_I$ into a
query $\bq_{I \ell h t} \in \mathbb{R}^{64}$, a set of keys $\bK_{I \ell h t} =
\{\bk_{I \ell h t i} \in \mathbb{R}^{64} \}_{i=1}^{49}$, and the corresponding
values $\bV_{I \ell h t} = \{ \bv_{I \ell h t i} \in \mathbb{R}^{64}
\}_{i=1}^{49}$:
\begin{IEEEeqnarray*}{lCl}
   \bq_{I\ell ht} &=& \bW_{I \ell h q} \, \bd_{\ell t} \\
   \bk_{I\ell h i} &=& \bW_{I \ell h k} \, \bx_{I i}
      \qquad \forall i \in \{1, 2, ..., 49\}\\
   \bv_{I \ell h i} &=& \bW_{I \ell h v} \, \bx_{I i}
      \qquad \forall i \in \{1, 2, ..., 49\}
\end{IEEEeqnarray*}
Then the attended image for each head is the weighted sum of the values, where
the weights are obtained from the dot product between the query and key:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{I \ell h t} &=& \sum_{i = 1}^{49}
      \text{softmax}\left(\bk_{I\ell h i}^T \, \bq_{I \ell ht} \right)
      \bv_{I \ell h i}
\end{IEEEeqnarray*}
The attention from each head is then concatenated into $\bx'_{I\ell t} \in
\mathbb{R}^{1024}$:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{I\ell t} &=& [\tx_{I\ell 1 t}, \tx_{I\ell 2 t}, ..., \tx_{I\ell 16 t}]
\end{IEEEeqnarray*}
and the overall image attention $\tx_{I\ell t} \in \mathbb{R}^{1024}$ is obtained
after adding a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tx_{I \ell t} &=& \text{LayerNorm}(\bd_{\ell t} + \bx'_{I\ell t})
\end{IEEEeqnarray*}
We use the same attention mechanism (with different weight matrices) to obtain
the attended article $\tx_{T \ell}$ and the attended face $\tx_{F \ell}$. These
three are finally concatenated and fed through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \tx_{C \ell t} &=& [\tx_{I \ell}, \tx_{T \ell t}, \tx_{F \ell}] \\
   \tx_{R \ell t} &=& \bW_{C \ell} \, \tx_{C \ell t} + \bb_{C \ell} \\
   \tx_{D \ell t} &=& \text{ReLU}(\bW_{R \ell} \, \tx_{R \ell t} + \bb_{R \ell} )\\
   \bz_{\ell + 1,t} &=& \text{LayerNorm}(\tx_{R \ell t} + \bW_{D \ell} \,
      \tx_{D \ell t} + \bb_{D \ell})
\end{IEEEeqnarray*}
The final output $\bz_{\ell + 1,t} \in \mathbb{R}^{1024}$ is used as the input
to the next transformer block, or if we are in the last block, it is used
to compute the logits over the token vocabulary.

\subsection{Bag of Tricks}
\label{ssec:bag_of_tricks}
